---
title: "TidyTuesday 2023-05-09: Childcare Costs"
author: "Zhuo Ding"
date: "2025-11-01"
output:
  word_document: default
  html_document: default
---

```{r}

library(tidyverse)



```

## Brief description of the dataset: The dataset titled “Childcare Costs” (TidyTuesday Week 19, 2023) explores economic and demographic patterns related to childcare affordability in U.S. counties. It contains over 34,000 observations and 61 variables from the U.S. Department of Labor’s “Women’s Bureau” and Census data. The dataset includes unemployment rates, median household income, childcare prices, and labor force participation for parents with children under 6. It helps researchers examine how family work patterns, income, and childcare costs vary across counties and years.

```{r}
childcare_costs <- readr::read_csv(
  "https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2023/2023-05-09/childcare_costs.csv"
)

str(childcare_costs)

```
```{r}
# Load tidyverse
library(tidyverse)

# Focus on infant childcare costs by year(mc_infant column is weekly, median price charged for Center-based Care for infants)
infant_cost_trend <- childcare_costs %>%
  group_by(study_year) %>%
  summarize(
    avg_infant_cost = mean(mc_infant, na.rm = TRUE)
  )

ggplot(infant_cost_trend, aes(x = study_year, y = avg_infant_cost)) +
  geom_point(color = "steelblue", size = 1.2) +
  labs(
    title = "Average Infant Childcare Cost (2008–2018)",
    x = "Year",
    y = "Average Annual Cost (USD)",
    caption = "Source: TidyTuesday 2023-05-09 Childcare Costs Dataset"
  ) 


```

##The plot shows the increasing in average weekly cost childcare costs for infants from 2008 to 2018. This indicates that childcare has become increasingly expensive over the decade. Such rising costs can bring difficulties to working families—especially those with lower incomes—and highlight the importance of childcare subsidies or supported programs.




